A thesis draft

### 2018-11-27 res/sections/15-ArchitecturalImplementation.tex
Add images as required

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.5]{Attempt1}
  \caption[Fist attempt components organization schema]{Fist attempt components
    organization schema. We can see how the main Openstack role is to deploy and
    manage the resources, while Openbaton has the role of maangement and
    orchestration. Finally, RabbitMQ sends and receives status update from the
    EMS for every VNF deployed.}
  \label{chap:archimpl:sec:fistattempt:img:schema1}
\end{figure}

@@

\paragraph*{Taker}
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.3]{tacker_architecture}
  \caption[Taker architecture schema]{Taker architecture
    schema~\cite{tackerOpenstackwiki}}
\end{figure}
Tacker is a VNFM and a NFVO. It is an official Openstack module, and it has the
ability to deploy, edit, stop and do periodic health checks VNF directly on it.
The develpers claim it has the possbility to make deployments to platforms
compatible with Openstack too. It supports VNF definition through the TOSCA
standard, and a proposal for SFC integration has been proposed in
2015~\cite{tackerOpenstackwiki}.

@@

\subsubsection{Scalability considerations}
When adopting Kubernetes, we realized the possibility to make every component
easily scalable. Indeed, all the following components can be described in
Kubernetes as a \verb!Service!. For a \verb!Service! a \verb!ReplicaSet! and a
consequent \verb!Deployment! can be associated, giving the possibility for it to
scale under heavy workloads. The introduction of scalability meant that was not
possible to refer to the components based on their IP, but we had to refer to
their service name. As it will be explained later, this introduced challenges
especially for the ingress and egress points of our network, that have to keep a
connection with the sender and the receiver. On top of that, the scalability and
the required DNS lookup meant a possible bottleneck. With a great number of
components and VNFs constantly quering the centralized Kubernetes DNS lookup
system a performance degradation could have easily happened. We decided to
distribute the DNS service too, integrating the CoreDNS Kubernetes default
service with \emph{DNSMasq}, a DNS server able to perform query caching for
faster name resolutions. We created a DNSMasq \verb!DaemonSets!, which in turn
deployed one Pod with DNSMasq running inside for every minion in the cluster. At
the time of the VNF launch, we set that the DNS resolution should pass first for
the local \verb!DNSMasq! DNS, and then for the Kubernetes CoreDNS service. In
this way, we were able to distribute the DNS query workload from the master,
using a local caching system to speed up the name resolution between services.

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.5]{Architecture}
  \caption[Architecture schema depicting the expected
    implementation]{Architecture schema depicting the expected implementation.
    It is possible to see how Openbaton interacts with the various components in
    the architecture, and how RabbitMQ is used as a message broker between the
    different parts to enable message exchanging.}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.5]{Attempt1}
  \caption[Fist attempt components organization schema]{Fist attempt components
    organization schema. We can see how the main Openstack role is to deploy and
    manage the resources, while Openbaton has the role of maangement and
    orchestration. Finally, RabbitMQ sends and receives status update from the
    EMS for every VNF deployed.}
  \label{chap:archimpl:sec:fistattempt:img:schema1}
\end{figure}

@@

\paragraph*{Taker}
\begin{figure}[t]
  \centering
  \includegraphics[scale=0.3]{tacker_architecture}
  \caption[Taker architecture schema]{Taker architecture
    schema~\cite{tackerOpenstackwiki}}
\end{figure}
Tacker is a VNFM and a NFVO. It is an official Openstack module, and it has the
ability to deploy, edit, stop and do periodic health checks VNF directly on it.
The develpers claim it has the possbility to make deployments to platforms
compatible with Openstack too. It supports VNF definition through the TOSCA
standard, and a proposal for SFC integration has been proposed in
2015~\cite{tackerOpenstackwiki}.

@@

\subsubsection{Scalability considerations}
When adopting Kubernetes, we realized the possibility to make every component
easily scalable. Indeed, all the following components can be described in
Kubernetes as a \verb!Service!. For a \verb!Service! a consequent
\verb!Deployment! can be associated, giving the possibility for it to scale
under heavy workloads. The introduction of scalability meant that was not
possible to refer to the components based on their IP, but we had to refer to
their service name. As it will be explained later, this introduced challenges
especially for the ingress and egress points of our network, that have to keep a
connection with the sender and the receiver. On top of that, the scalability and
the required DNS lookup meant a possible bottleneck. With a great number of
components and VNFs constantly quering the centralized Kubernetes DNS lookup
system a performance degradation could have easily happened. We decided to
distribute the DNS service too, integrating the CoreDNS Kubernetes default
service with \emph{DNSMasq}, a DNS server able to perform query caching for
faster name resolutions. We created a DNSMasq \verb!DaemonSets!, which in turn
deployed one Pod with DNSMasq running inside for every minion in the cluster. At
the time of the VNF launch, we set that the DNS resolution should pass first for
the local \verb!DNSMasq! DNS, and then for the Kubernetes CoreDNS service. In
this way, we were able to distribute the DNS query workload from the master,
using a local caching system to speed up the name resolution between services.
